\begin{abstract}

\noindent\textbf{Background:} The global transition toward renewable energy sources has accelerated the need for efficient peer-to-peer (P2P) energy trading mechanisms. Traditional centralized utility models are inadequate for managing bidirectional energy flows between prosumers---consumers who also produce energy through distributed generation systems such as rooftop solar panels.

\vspace{0.3cm}

\noindent\textbf{Objective:} This thesis presents \gridtokenx{}, a blockchain-based platform designed for real-time P2P energy trading in permissioned microgrid environments. The platform leverages \solana{}'s high-performance architecture with Proof of Authority (PoA) consensus to achieve throughput characteristics suitable for production energy markets.

\vspace{0.3cm}

\noindent\textbf{Methodology:} We evaluate \gridtokenx{} using TPC benchmarks adapted for blockchain technology, following the ``blockchainification'' methodology established at TPC Technology Conferences. Our comprehensive evaluation encompasses TPC-C (order processing), TPC-E (trading simulation), TPC-H (analytical queries), and Smallbank (contention stress testing) workloads.

\vspace{0.3cm}

\noindent\textbf{Results:} Key performance findings demonstrate that \gridtokenx{} achieves:
\begin{itemize}
  \item \textbf{21,101 \tpmc{}} on TPC-C style energy order workloads (352 TPS equivalent)
  \item \textbf{1,741 TPS} on Smallbank consensus stress tests
  \item \textbf{11.30ms average latency} with sub-20ms p99 response times
  \item \textbf{99.9\% transaction success rate} under sustained load
  \item \textbf{Linear scalability} up to 200 concurrent prosumer accounts
\end{itemize}

\vspace{0.3cm}

\noindent\textbf{Conclusions:} The measured \textit{Trust Premium} of 5.65$\times$ compared to centralized PostgreSQL represents an acceptable performance trade-off for applications requiring decentralized trust, tamper-proof audit trails, and automated settlement. These results demonstrate that Solana-based blockchain with PoA consensus provides viable, production-ready performance characteristics for real-time P2P energy trading applications in smart grid environments.

\vspace{0.5cm}

\noindent\textbf{Keywords:} Blockchain, Peer-to-Peer Energy Trading, Solana, Anchor Framework, TPC Benchmark, Proof of Authority, Smart Grid, Prosumer, Performance Evaluation, Distributed Ledger Technology

\end{abstract}
